ps4_models

### 2020-10-28 bi-model.Rmd
bi model

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)

@@

@@

```
```{r}
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.9)

training <- data[0:boundary,]
model <- nnet::multinom(vote_2020 ~ state + race_ethnicity + gender + 
                          household_income + education, data = training)
```

>>>>

```{r}
library(haven)
library(tidyverse)
library(nnet)
library(Metrics)
library(brms)
```
```{r}
remove.packages("rstan")

```{r}
# install.packages("rstan", repos = "https://cloud.r-project.org/", dependencies = TRUE)

@@

reduced_data <- reduced_data[reduced_data$vote_2020 == "Donald Trump" |
                             reduced_data$vote_2020 == "Joe Biden",]

@@

reduced_data
```
```{r}
shuffle_indices <- sample(total_rows)
data <- reduced_data[shuffle_indices,]
boundary <- as.integer(total_rows*0.9)

training <- data[0:boundary,]
model <- brms::brm(formula = vote_2020 ~ state + race_ethnicity + gender + 
                          household_income + education, 
                   data = training,
                   family = bernoulli(link = "logit"),
                   warmup = 500, 
                   iter = 4000, 
                   chains = 2, 
                   inits= "0", 
                   cores=2,
                   seed = 123
                   )
```
